Spectral-Spatial Hyper-spectral Image Classification Using Dual-Channel Capsule Networks

### 2020-03-12 paper/paper.tex
fixed some bugs

	\section{EXPERIMENT}\label{sec:experiment}
	In this section, we showed and analyzed the training result.
	We compared our model with six neural network based algorithms i.e.,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{sharma2016hyperspectral},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	the CapsNet that is identical to our DCCN model except the spectral channel, and the machine learning algorithm
	SVM\@.
	The competing neural network based algorithms are trained using the best network structure and hyper-parameters
	proposed by the authors in their papers, and the SVM algorithm was trained using 10\% of the total labeled pixels
	as the DCCN model.
	The accuracy metrics we used include overall accuracy(OA), average accuracy(AA) and Kappa Coefficient($\kappa$).

	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
	Pavia University(PU) dataset, the Pavia Center(PC) dataset, the Salinas Valley(SV) dataset and the Salinas A(SA)
	dataset, which is a small subset of the Salinas Valley dataset.
	The first three of them are relatively large dataset and the last one is relatively small.
	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
	Here follows the brief introduction of the four dataset(see table\ref{psgt}).
	\begin{enumerate}[1)]
		\item \textit{Pavia Center and University} These are two scenes acquired by the ROSIS sensor during a flight
		campaign over Pavia, northern Italy.
		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
		Pavia Centre is a 1096*1096 pixels image, and Pavia University is 610*610 pixels, but some of the samples in
		both images contain no information and have to be discarded before the analysis, so the final picture size is
		1096*715 and 610*340.
		The geometric resolution is 1.3 meters.
		Both image has 9 different ground truth classes each.
		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
		California, and is characterized by high spatial resolution (3.7-meter pixels).
		The Salinas Valley dataset is a 512*217 pixels image, and the Salinas A is a subset of the Salinas Valley
		containing 86*83 pixels.
		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
		bands left in both of the tow dataset.
		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes.
	\end{enumerate}
	\begin{table}[h]
		\centering
		\tiny
		\resizebox{\textwidth}{!}{
			\begin{tabular}{|c|c|c|c|}

@@

	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
	First of all, we listed the quantitative classification assessment using the PU, PC, SV and SA dataset considering
	SVM,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{sharma2016hyperspectral},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	CapsNet and DCCN together in table~\ref{result}.
	From the results reported in table~\ref{result}, we can observe that our proposed DCCN model outperforms all the
	other seven state-of-art models on all 4 dataset.
	Among all competitors in this experiment, 3D CNN\cite{hamida20183} and the CapsNet model performed relatively second
	best, since both of the two model achieved second high accuracy on different dataset.
	This is expected because both of the two algorithm are spectral-spatial based so they can utilize more information,
	compared to the 2D CNN, FCN, SVM and CNN-MRF classifiers, to classify the HSI pixels.
	Nevertheless, our DCCN model can consistently outperform the second-best algorithm with an average \textbf{fill data
	here} for AA, OA, $\kappa$.

	\begin{table}[htb]
		\tiny
		\centering
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			 &\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
			\hline
			\begin{tabular}{c}
				\textbf{model}\\
				\hline
				{SVM}\\
				{1D CNN\cite{hu2015deep}}\\
				{2D CNN\cite{sharma2016hyperspectral}}\\
				{3D CNN\cite{hamida20183}}\\
				{3D FCN\cite{lee2016contextual}}\\
				{CNN-MRF\cite{cao2018hyperspectral}}\\
				{CapsNet}\\
				{DCCN}\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}\\
			\hline
		\end{tabular}
		\caption{Final result of all adopted models.}
		\label{result}
	\end{table}

@@

		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}

@@

		\begin{subfigure}{0.125\textwidth}
			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}

@@

	\section{DISCUSSION}\label{sec:discussion}
	In this sector, we further explored the effect of different hyper-parameters to the DCCN\@.
	We used the Pavia University and Salinas A dataset to train and test our model, so that we can observe the model's
	performance on both large and small dataset.
	We first tested the effect of different size of training set with a fixed patch size of 7*7, and then tested the
	effect of

>>>>

	\section{EXPERIMENT}\label{sec:experiment}
	In this section, we showed and analyzed the training result.
	We compared our model with six neural network based algorithms i.e.,
	semi-supervised 2D CNN\cite{liu2017semi},
	3D CNN\cite{hamida20183},
	multi-scale 3D CNN(3D CNN-MS)\cite{he2017multi},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	the CapsNet that is identical to our DCCN model except the spectral channel, and the machine learning algorithm
	SVM\@.
	The competing neural network based algorithms are trained using the best network structure and hyper-parameters
	proposed by the authors in their papers, and the SVM algorithm was trained using 10\% of the total labeled pixels
	as the DCCN model.
	In order to reduce the effect of accidental errors, we did the same experiment with identical parameters five times
	on each model.
	The accuracy metrics we used include overall accuracy(OA), average accuracy(AA) and Kappa Coefficient($\kappa$).

	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
	Pavia University(PU) dataset, the Pavia Center(PC) dataset, the Salinas Valley(SV) dataset and the Salinas A(SA)
	dataset, which is a small subset of the Salinas Valley dataset.
	The first three of them are relatively large dataset and the last one is relatively small.
	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
	Here follows the brief introduction of the four dataset(see table\ref{psgt}).
	\begin{enumerate}[1)]
		\item \textit{Pavia Center and University} These are two scenes acquired by the ROSIS sensor during a flight
		campaign over Pavia, northern Italy.
		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
		Pavia Centre is a 1096×1096 pixels image, and Pavia University is 610×610 pixels, but some of the samples in
		both images contain no information and have to be discarded before the analysis, so the final picture size is
		1096×715 and 610×340.
		The geometric resolution is 1.3 meters.
		Both image has 9 different ground truth classes each.
		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
		California, and is characterized by high spatial resolution (3.7-meter pixels).
		The Salinas Valley dataset is a 512×217 pixels image, and the Salinas A is a subset of the Salinas Valley
		containing 86×83 pixels.
		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
		bands left in both of the tow dataset.
		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes.
	\end{enumerate}
	\begin{table}[h]
		\centering
		\tiny
		\resizebox{\textwidth}{!}{
			\begin{tabular}{|c|c|c|c|}

@@

	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
	First of all, we listed the quantitative classification assessment using the PU, PC, SV and SA dataset considering
	SVM,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{liu2017semi},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	CapsNet and DCCN together in table~\ref{result}.
	From the results reported in table~\ref{result}, we can observe that our proposed DCCN model outperforms all the
	other seven state-of-art models on all 4 dataset.
	Among all competitors in this experiment, 3D CNN\cite{hamida20183} and the CapsNet model performed relatively second
	best, since both of the two model achieved second high accuracy on different dataset.
	This is expected because both of the two algorithm are spectral-spatial based so they can utilize more information,
	compared to the 2D CNN, FCN, SVM and CNN-MRF classifiers, to classify the HSI pixels.
	Nevertheless, our DCCN model can consistently outperform the second-best algorithm with an average \textbf{fill data
	here} for AA, OA, $\kappa$.

	\begin{table}[htb]
		\tiny
		\centering
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			 &\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
			\hline
			\begin{tabular}{c}
				\textbf{model}\\
				\hline
				{SVM}\\
				{1D CNN\cite{hu2015deep}}\\
				{2D CNN\cite{liu2017semi}}\\
				{3D CNN\cite{hamida20183}}\\
				{3D FCN\cite{lee2016contextual}}\\
				{CNN-MRF\cite{cao2018hyperspectral}}\\
				{CapsNet}\\
				{DCCN}\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}\\
			\hline
		\end{tabular}
		\caption{Final result of all adopted models.}
		\label{result}
	\end{table}

@@

		\begin{subfigure}{0.12\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/predictMap.eps}

@@

		\begin{subfigure}{0.12\textwidth}
			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/probMap.eps}

@@

	\section{DISCUSSION}\label{sec:discussion}
	In this sector, we further explored the effect of different hyper-parameters to the DCCN\@.
	We used the Pavia University and Salinas A dataset to train and test our model, so that we can observe the model's
	performance on both large and small dataset.
	We first tested the effect of different size of training set with a fixed patch size of 7×7, and then tested the
	effect of different patch sizes.
